### 2017-12-29 Paper/examples.tex
work in progess
added screening plot for borehole

As mentioned earlier in this section, cheap function evaluations of the discharge using 
Eq.~\ref{eq:bore} enable us to compute converged estimates of $\mathcal{T}(\theta_i)$. Plotted in
Figure~\ref{fig:sense_bore} are estimates of these indices corresponding to the uncertain
parameters in the borehole function.

>>>>

As mentioned earlier in this section, cheap function evaluations of the discharge using 
Eq.~\ref{eq:bore} enable us to compute converged estimates of $\mathcal{T}(\theta_i)$. Plotted in
Figure~\ref{fig:sense_bore} are estimates of these indices corresponding to the uncertain
parameters in the borehole function using 10$^6$ pseudo-random
samples in the input parameter domain. These estimates are used to verify fidelity of
parameter screening based on the methodology presented in Section~\ref{sec:method}. 
In Figure~\ref{fig:screen_bore}, we plot estimates of the screening parameter ($\hat{\mathcal{C}_i\mu_i}$)
for a wide range of the number of samples used for approximating $\mu_i$ using Eq.~\ref{eq:mu}.
Estimates for $\hat{\mathcal{C}_i\mu_i}$ are found to be in excellent agreement with $\mathcal{T}(\theta_i)$
even when small number of samples are used to estimate the expectation in Eq.~\ref{eq:mu}. 
Consequently, the relative importance of uncertain 
parameters in the borehole function is found to be consistent with predictions based on the Sobol' index.
